Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2020-07-28 RSVOptimization.rnw
Removed rogue list of tables/figures
Adjustments for Pediatrics word limits

\newcommand\frontmatter{
    \corrfull{Address correspondence to}{Ben Artin, 350 George St, Room C323, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
    \frontmattersection{Short title}{\headertitle}
    \frontmattersection{Conflict of interest disclosures}{Virginia E. Pitzer has received reimbursement from Merck and Pfizer for travel expenses to Scientific Input Engagements related to RSV vaccines. Daniel M. Weinberger has received consulting fees from Pfizer, Merck, GSK, and Affinivax for topics unrelated to this manuscript and is the Principal Investigator on a research grant from Pfizer on an unrelated topic. Ben Artin reports no relevant conflicts.}
    \frontmattersection{Funding}{This study was funded by the NIH/NIAID grant R01AI137093.}
    \frontmattersection{Role of funder}{The NIH had no role in the design and conduct of the study.}
    \frontmattersection{IRB approval}{This study was approved by the IRB at Yale School of Medicine and the HIC at the Connecticut Department of Public Health.}
    \frontmattersection{Data sharing}{Deidentified hospitalization data can be requested from the Connecticut Department of Public Health. The analysis code is available at \url{https://github.com/weinbergerlab/rsv-ct-optimization}.}
    \frontmattersection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
    \frontmattersection{Article summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
    \frontmattersection{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide. RSV chemoprophylaxys is expensive. In the US, the prophylaxis schedule recommendation is published by the AAP. The AAP recommens the same schedule for all states other than Florida.}
    \frontmattersection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
    \clearpage
    \frontmattersection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript. Daniel M. Weinberger obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript. Virginia E. Pitzer reviewed and revised the manuscript. All authors approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}
    \clearpage
}

@@

\abstractsection{Background and Objectives}{RSV causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants. Palivizumab provides safe and effective, yet costly, immunoprophylaxis. The AAP recommends palivizumab only for high-risk infants and only during the RSV season. Outside of Florida, the current guidelines do not recommend regional adjustments to the timing of the immunoprophylaxis regimen. Our hypothesis is that adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence can reduce the disease burden compared to the current AAP-recommended RSV prophylaxis regimen.}

\abstractsection{Methods}{We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}. We estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines. We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates, but unchanged duration.}

@@

\abstractsection{Conclusions}{Initiating RSV prophylaxis based on state-level data may improve protection compared with the standard AAP recommendations. In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.}

@@

%\listoftables
%\clearpage

% \listoffigures
% \clearpage

>>>>

\newcommand\frontmatter{
    \corrfull{Address correspondence to}{Ben Artin, 350 George St, Room C323, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
    \frontmattersection{Short title}{\headertitle}
    \frontmattersection{Conflict of interest disclosures}{Virginia E. Pitzer has received reimbursement from Merck and Pfizer for travel expenses to Scientific Input Engagements related to RSV vaccines. Daniel M. Weinberger has received consulting fees from Pfizer, Merck, GSK, and Affinivax for topics unrelated to this manuscript and is the Principal Investigator on a research grant from Pfizer on an unrelated topic. Ben Artin reports no relevant conflicts.}
    \frontmattersection{Funding}{This study was funded by the NIH/NIAID grant R01AI137093.}
    \frontmattersection{Role of funder}{The NIH had no role in the design and conduct of the study.}
    \frontmattersection{IRB approval}{This study was approved by the IRB at Yale School of Medicine and the HIC at the Connecticut Department of Public Health.}
    \frontmattersection{Data sharing}{Deidentified hospitalization data can be requested from the Connecticut Department of Public Health. The analysis code is available at \url{https://github.com/weinbergerlab/rsv-ct-optimization}.}
    \frontmattersection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
    \frontmattersection{Article summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
    \frontmattersection{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide. RSV chemoprophylaxys is expensive. In the US, the AAP recommends the same schedule for all states other than Florida.}
    \frontmattersection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to Connecticut, with no additional benefit when applied to counties within Connecticut.}
    \clearpage
    \frontmattersection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript. Daniel M. Weinberger obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript. Virginia E. Pitzer reviewed and revised the manuscript. All authors approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}
    \clearpage
}

@@

\abstractsection{Background and Objectives}{RSV causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants. Palivizumab provides safe and effective, yet costly, immunoprophylaxis. The AAP recommends palivizumab only for high-risk infants and only during the RSV season. Outside of Florida, the current guidelines do not recommend regional adjustments to the timing of the immunoprophylaxis regimen. Our hypothesis is that adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence can reduce the disease burden compared to the current AAP-recommended prophylaxis regimen.}

\abstractsection{Methods}{We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}. We estimated the fraction of all Connecticut RSV cases occurring during the period of protection offered by immunoprophylaxis (``preventable fraction'') under the AAP guidelines. We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates, but unchanged duration.}

@@

\abstractsection{Conclusions}{Initiating RSV prophylaxis based on state-level data may improve protection compared with the AAP recommendations. In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.}

@@
